Effort and Delay Discounting in a Foraging Environment

### 2018-10-11 Cost2_prereg.Rmd
Cleaning up code and improving figures

## Miscelaneous
lbls <- c("Wait","Cognitive","Physical","Easy")
cols = c("#78AB05","#D9541A","deepskyblue4", "grey50") # plot colors (wait, effort)
lthick = 2 # line thickness for plots

@@

# load cognitive effort group
setwd('/Volumes/Addon/Grad school/Cost2_data/cog')
temp = list.files(pattern="*.csv")
cogDataLong = lapply(temp, read.csv, header = FALSE)

@@

# plot
p2 <- ggplot(summaryData, aes(x=Group, y=propComplete, fill = Group))
p2 <- p2 + geom_boxplot(show.legend = F) +
    scale_fill_manual(values = cols) +
    labs(title = "Proportion Completed by Group", y="Proportion Completed") +
    theme_classic()

@@

``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
### THE PLOTS FOR YALE
# Ggplot made plotting way easier than the previous version
# This is in case you don't want to plot the easy condition (easier to see)
trueProp2 <- trueProp[-(28:36), ]

a1 <- ggplot(data = trueProp, aes(x=interaction(Reward, Handling), y=propComplete, color=Group)) + 
        geom_point(size=3) + 
        geom_errorbar(aes(ymin=propComplete-SE, ymax=propComplete+SE), width=0.2, size=1) +
        geom_line(aes(group = interaction(Handling, Group)), size=1) +
        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey48", color = "grey48", size = 3, show.legend = F) +
        labs(x = "Reward.Handling", y = "Proportion Accepted", title = "Proportion Accepted per Handling and Reward Combination") +
        scale_color_manual(values=cols) +
        theme_classic()

@@

``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
# RTs
# let's try to do some survival curves
RTW <- numeric() # vector of all decision-related RTs for the wait group
RTC <- numeric() # same for the cog group
RTP <- numeric()
RTE <- numeric()

# Wait group
for (subj in seq(nSubsW)){

    # index for trials quit
    tempChoiceW <- waitData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTW <- c(RTW,waitData[[subj]]$RT[tempChoiceW])

# Cognitive group
for (subj in seq(nSubsC)){

    # index for trials quit
    tempChoiceC <- cogData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTC <- c(RTC,cogData[[subj]]$`Choice RT`[tempChoiceC])

# Physical group
for (subj in seq(nSubsP)){

    # index for trials quit
    tempChoiceP <- physData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTP <- c(RTP,physData[[subj]]$RT[tempChoiceP])

# Pheaysical group
for (subj in seq(nSubsE)){

    # index for trials quit
    tempChoiceE <- easyData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTE <- c(RTE,easyData[[subj]]$RT[tempChoiceE])

# create an array with both data (for surv fit autoplot trials)
lenC <- length(RTC)
lenW <- length(RTW)
lenP <- length(RTP)
lenE <- length(RTE)

RTgroups <- c(rep("Wait",lenW), 
              rep("Effort",lenC), 
              rep("Physical",lenP),
              rep("Easy",lenE))
RTall <- c(RTW,RTC,RTP,RTE)

# plot ecdf 
ecdfW <- ecdf(RTW)
ecdfC <- ecdf(RTC)
ecdfP <- ecdf(RTP)
ecdfE <- ecdf(RTE)

range <- seq(0,10, by = 0.001)

plot(range,ecdfW(range),
     type = "l",
     main = "ECDF and CIs for the Response Times",
     xlab = "Seconds",
     ylab = "ECDF",
     xlim = c(0,5),
     col = cols[1],
     bty = "n",
     lwd = lthick)
lines(range,
      ecdfC(range),
      col = cols[2],
      lwd = lthick)
lines(range,
      ecdfP(range),
      col = cols[3],
      lwd = lthick)
lines(range,
      ecdfE(range),
      col = cols[4],
      lwd = lthick)
legend("right",
       lbls,
       fill = cols,
       cex = 0.8)

# and CIs for each (unnecessary unless I end up plotting)
CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
CIC <- median(CIC) - (quantile(CIC,0.025))
CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIW <- median(CIW) - (quantile(CIW,0.025))
CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIP <- median(CIP) - (quantile(CIP,0.025))
CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIE <- median(CIE) - (quantile(CIE,0.025))
lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)

# just cause, Kolmogrov-Smirnov 
# ksRT <- ks.test(RTW,RTC)
# RTPerm <- permute(RTW,RTC)
# RTCohen <- cohenD(RTW,RTC)

rm(lenC,lenW,lenP,lenE)

>>>>

## Miscelaneous
lbls <- c("Wait","Cognitive","Physical","Easy")
cols = c("#78AB05","#D9541A","deepskyblue4", "darkgoldenrod2") # plot colors (wait, effort)
lthick = 2 # line thickness for plots

@@

# load cognitive effort group
setwd('./data/Cost2_data/cog')
temp = list.files(pattern="*.csv")
cogDataLong = lapply(temp, read.csv, header = FALSE)

@@

# plot
p2 <- ggplot(summaryData, aes(x=Group, y=propComplete, fill = Group))
p2 <- p2 + geom_boxplot(show.legend = F) +
    scale_fill_manual(values = cols) +
    ylim(c(0,1)) +
    labs(title = "Proportion Completed by Group", y="Proportion Completed") +
    theme_classic()

@@

``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
### THE PLOTS FOR YALE
# Ggplot made plotting way easier than the previous version
# This is in case you don't want to plot the easy condition (easier to see)
cols = c("#78AB05","#D9541A","deepskyblue4", "grey50")
trueProp2 <- trueProp[-(28:36), ]

a1 <- ggplot(data = trueProp, aes(x=interaction(Reward, Handling), y=propComplete, color=Group)) + 
        geom_point(size=3) + 
        geom_errorbar(aes(ymin=propComplete-SE, ymax=propComplete+SE), width=0.2, size=1) +
        geom_line(aes(group = interaction(Handling, Group)), size=1) +
        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Reward.Handling", y = "Proportion Accepted", title = "Proportion Accepted per Handling and Reward Combination") +
        scale_color_manual(values=cols) +
        theme_classic()

@@

``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# RTs
# let's try to do some survival curves
RTW <- unlist(lapply(waitData, function(data) {data$RT[data$Choice==0]})) # vector of all decision-related RTs for the wait group
RTC <- unlist(lapply(cogData, function(data) {data$`Choice RT`[data$Choice==0]})) # same for the cog group
RTP <- unlist(lapply(physData, function(data) {data$RT[data$Choice==0]}))
RTE <- unlist(lapply(easyData, function(data) {data$RT[data$Choice==0]}))

# create a data frame for plotting
RTgroups <- c(rep("Wait",length(RTW)), rep("Effort",length(RTC)), rep("Physical",length(RTP)), rep("Easy",length(RTE)))
RTall <- c(RTW,RTC,RTP,RTE)
RTframe <- data.frame(RTgroups, RTall)

# plot
ggplot(RTframe, aes(RTall, color = RTgroups)) + 
  stat_ecdf(lwd = 1) + 
  scale_color_manual(values = cols) + 
  scale_x_continuous(breaks = seq(14)) +
  labs(title = "ECDFs for the Response Times", x = "Seconds", y = "ECDF") +
  theme_classic()

# # and CIs for each (unnecessary unless I end up plotting)
# CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
# CIC <- median(CIC) - (quantile(CIC,0.025))
# CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
# CIW <- median(CIW) - (quantile(CIW,0.025))
# CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
# CIP <- median(CIP) - (quantile(CIP,0.025))
# CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
# CIE <- median(CIE) - (quantile(CIE,0.025))
# lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
# lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
# lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
# lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
# lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
# lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
# lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
# lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)
